---
title: Preparing OD data for network generation with od2net
#| eval: false
#| echo: false
format: gfm
execute: 
  message: false
  warning: false
---

This R package provides functions to prepare OD data for network generation with the `od2net` tool, as illustrated in the example below.

## Example

Imagine you want to generate a route network with values on the links representing the number of pupils/parents on their way to school each school day. The following code shows how to prepare the data for the `od2net` tool.


```{r}
#| eval: false
# Install pak if not already installed:
if (!requireNamespace("pak", quietly = TRUE)) {
  install.packages("pak")
}
pak::pkg_install("robinlovelace/od2net/r@67-r-port")
dir.create("input", showWarnings = FALSE)
make_zones("https://github.com/acteng/netgen/raw/main/input/zones_york.geojson")
make_osm()
make_origins()
make_elevation()
destinations = destinations_york # Provided in the R package
names(destinations)[1] = "name"
destinations = destinations[1]
class(destinations$name) = "character"
sf::write_sf(destinations, "https://github.com/acteng/netgen/raw/main/input/destinations.geojson", delete_dsn = TRUE)
# Save the OD dataset:
od = od_geo |>
  sf::st_drop_geometry() |>
  transmute(from = O, to = as.character(D), count = round(trips_modelled))
readr::write_csv(od, "input/od.csv", quote = "all")
```

Then create a config.json file, e.g. with the following content:

```json
{
  "requests": {
    "description": "Test data for SchoolRoutes project.",
    "pattern": {
      "ZoneToPoint": {
        "zones_path": "zones.geojson",
        "destinations_path": "destinations.geojson",
        "csv_path": "od.csv",
         "origin_zone_centroid_fallback": false
      }
    },
    "origins_path": "buildings.geojson",
    "destinations_path": "destinations.geojson"
  },
  "cost": "Distance",
  "uptake": "Identity",
  "lts": "BikeOttawa",
  "elevation_geotiff": "elevation.tif"
}
```

Then run the following code to generate the network:

Run the tool with Docker as follows:


```{bash}
#| eval: false
# On Linux:
sudo docker run -v $(pwd):/app ghcr.io/urban-analytics-technology-platform/od2net:main /app/config.json
# or in Windows:
sudo docker run -v ${pwd}:/app ghcr.io/urban-analytics-technology-platform/od2net:main /app/config.json
```

```{r}
#| eval: false
#| echo: false
system("docker run -v $(pwd):/app ghcr.io/urban-analytics-technology-platform/od2net:main /app/config.json")
```

After that you should see the following in the output folder:

```{r}
#| eval: false
fs::dir_tree("output")
```

Helper functions

<details>

The following functions could be useful when you're preparing the data, and show the kind of data preparation that is required.

<!-- TODO: consider adding these functions to the package at some stage? -->

```{r}
# Aim: generate input data for od2net with R

#' Generate a 'zones.geojson' file
#' 
#' This function requires a zones file, e.g.
#' "https://raw.githubusercontent.com/nptscot/npt/main/data-raw/zones_edinburgh.geojson"
#' or a file on your computer.
#' It will generate a file in the input/ folder
#' 
#' @param file Location or URL of zones file
make_zones = function(file) {
  zones = sf::read_sf(file)[1]
  names(zones)[1] = "name"
  sf::write_sf(zones, "input/zones.geojson", delete_dsn = TRUE)
}

make_od = function() {
  od = readr::read_csv("https://raw.githubusercontent.com/nptscot/npt/main/data-raw/od_subset.csv")
  od = od |>
    dplyr::transmute(from = geo_code1, to = geo_code2, count = bicycle)
  readr::write_csv(od, "input/od.csv")
}
```

